### 2020-05-27 writeup/proof_examples.tex
lem B.1

The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that $\hat{v}$ is close to $1$.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ to show the result.
\end{itemize}

We denote
\begin{align}
	\val(w) &= n_1\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + n_2w^2\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + (n_1+n_2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
Under the setting of Proposition \ref{prop_model_shift_tight}, using concentration of random vector with i.i.d. Gaussian entries, Lemma \ref{largedeviation}, we have that
$$\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2})\right)\quad \text{with probability }1-\oo(1).$$
Thus it suffices to study the behavior of $\val (w)$.
For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.

\begin{lemma}\label{lem_hat_v}
Suppose the assumptions of Proposition \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. Then we have that the optimal ratio for $\val(w)$ satisfies
	\be\label{hatw_add1}|\hat w -1|=\OO(p^{-1}).\ee
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{lemma}
\begin{proof}
The proof is also similar to the one for Proposition \ref{thm_cov_shift}. First it is easy to observe that $\val(w)\le \val(-w)$ for $w\ge 0$. Hence it suffices to consider the $w\ge 0$ case.

We first consider the case $w\ge 1$. We write
\begin{align}
	\val(w) &= n_1\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + n_2\left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + \sigma^2(n_1+n_2) \cdot \bigtr{(w^{2}X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } .\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}

Taking derivative of $\val(w)$ with respect to $w$, we obtain that
\begin{align*}
\val'(w) \ge &~ n_1\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
+&~ n_2\left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
		-&~ 2(n_1+n_2) \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } = n_1 \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
\end{align*}
where the matrix $\cal A$ is
\begin{align*}
\cal A :&= \left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2. - 2\frac{n_1+n_2}{n_1}\frac{\sigma^2}{w^3}X_1^\top X_1
\end{align*}
Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
\begin{align*}
\cal A \succeq - \frac{4d^2}{w^5}(\sqrt{n_2}+\sqrt{p})^4 + \frac{n_2}{n_1} \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](\sqrt{n_1}-\sqrt{p})^4 - 2\frac{n_1+n_2}{n_1}\frac{\sigma^2}{w^3}(\sqrt{n_1}+\sqrt{p})^2\succ 0,
\end{align*}
as long as
$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{\kappa^2}\frac{(n_1+n_2)(\sqrt{n_1}+\sqrt{p})^2}{n_2(\sqrt{n_1}-\sqrt{p})^4}+ \frac{2d^2}{\kappa^2}\frac{n_1(\sqrt{n_2}+\sqrt{p})^4}{n_2(\sqrt{n_1}-\sqrt{p})^4}.$$
Hence $\val'(w)>0$ on $(w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>w_1$. Hence we must have $\hat w\le w_1$. Note that under our assumptions, we have $w_1=1+\OO(p^{-1})$.

Then we consider the case $w\le 1$. Taking derivative of $\val(w)$ with respect to $w$, we obtain that
\begin{align}
	\val'(w) &\le n_1 \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + n_2\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& = n_1 \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
\end{align}
where the matrix $\cal B$ is
$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{n_2}{n_1}\left[2d^2w +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2.$$
Using the estimate \eqref{eq_isometric}, we get that $\cal B$ is upper bounded as
\begin{align*}
\cal B \preceq - 2(1-w)\kappa^2(\sqrt{n_2}-\sqrt{p})^4 +2d^2 w\frac{n_2}{n_1}(\sqrt{n_1}+\sqrt{p})^4 \prec 0,
\end{align*}
as long as
$$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{n_2(\sqrt{n_1}+\sqrt{p})^4}{n_1(\sqrt{n_2}-\sqrt{p})^4}.$$
Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly increasing for $w<w_2$. Hence we must have $\hat w\le w_2$. Note that under our assumptions, we have $w_2=1-\OO(p^{-1})$.
\end{proof}

>>>>

For the ratio $w=w_1/w_2$, we define the function
\begin{align}
	\val(w) &= n_1\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + n_2w^2\left[d^2 +\left( w-1\right)^2\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + (n_1 w^2 +n_2)\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
Under the setting of Lemma \ref{prop_model_shift_tight}, again using concentration for random vectors with i.i.d. entries, Lemma \ref{largedeviation}, we can obtain that for the validation loss in \eqref{eq_val_mtl},
\be\label{boundv-w}\val(\hat{B}; w_1, w_2)= \val(w) \left( 1+\OO(p^{-1/2+\e})\right)\ee
with high probability for any constant $\e>0$. Thus for the following discussions, it suffices focus on the behavior of $\val (w)$. Let $\hat w$ the minimizer of $\val(w)$. The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that the optimal ratio $\hat{w}$ is close to $1$. Then \eqref{boundv-w} gives that $|\hat v - \hat w|=\OO(p^{-1/2+\e})$ whp.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
\end{itemize}
%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
For the first step, we will prove the following result.
\begin{lemma}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
We have that the minimizer for $\val(w)$ satisfies
	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\ee
	for some constant $C>0$.
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{lemma}
\begin{proof}
First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$.

We first consider the case $w\ge 1$. We write
\begin{align}
	\val(w) &= n_1\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + n_2\left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + n_1\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ n_2\sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
Notice that 
$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
are increasing functions in $w$. Hence taking derivative of $\val(w)$ with respect to $w$, we obtain that
\begin{align*}
\val'(w) \ge &~ n_1\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
+&~ n_2\left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
		-&~ 2 n_2 \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } = n_2 \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
\end{align*}
where the matrix $\cal A$ is
\begin{align*}
\cal A :&= \frac{n_1}{n_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
\end{align*}
Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
\begin{align*}
\cal A \succeq&~ - \frac{4d^2}{w^5}n_1n_2 (\al_+(\rho_2)+\oo(1))^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]n_1^2 (\al_-(\rho_1)-\oo(1))^2 \\
&~ - 2 \frac{\sigma^2}{w^3}n_1(\al_{+}(\rho_1)+\oo(1)) \succ 0,
\end{align*}
as long as
$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
Hence $\val'(w)>0$ on $(w_1,\infty)$, i.e. $\val(w)$ is strictly increasing for $w>w_1$. Hence we must have $\hat w\le w_1$.

Then we consider the case $w\le 1$, and the proof is similar as above. Taking derivative of $\val(w)$, we obtain that
\begin{align}
	\val'(w) &\le n_1 \left[2\left( w-1\right) \kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + n_2\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right]\cdot \tr\left[( w^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
	&~ + n_1(2 w\sigma^2) \cdot \bigtr{(w^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-2} X_2^\top X_2  }\\
			& = n_1 \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} \cal B} , \nonumber
\end{align}
where the matrix $\cal B$ is
$$\cal B= 2\left( w-1\right) \kappa^2  (X_2^{\top}X_2)^2+\frac{n_2}{n_1}\left[2wd^2 +2w\left( w-1\right)(2w-1)\kappa^2\right](X_1^{\top}X_1)^2 + 2 w\sigma^2 X_2^\top X_2 .$$
Using the estimate \eqref{eq_isometric}, we get that $\cal B$ is upper bounded as
\begin{align*}
\cal B \preceq - 2(1-w)\kappa^2 n_2^2 (\al_-(\rho_2) -\oo(1))^2 +2w d^2 n_1n_2 (\al_+(\rho_1) +\oo(1))^2 + 2w\sigma^2 n_2 (\al_+(\rho_2)+\oo(1)) \prec 0,
\end{align*}
as long as
$$w< w_2:=1 -   \frac{d^2}{\kappa^2}\frac{\rho_1(\al_+(\rho_1) +\oo(1))^2}{\rho_2 \al_-^2(\rho_2) } -  \frac{\sigma^2}{n_2\kappa^2}\frac{\al_{+}(\rho_2)+\oo(1)}{\al_{-}^2(\rho_2)} .$$
Hence $\val'(w)<0$ on $[0,w_2)$, i.e. $\val(w)$ is strictly decreasing for $w<w_2$. Hence we must have $\hat w\le w_2$.

In sum, we obtain that $w_2\le w\le w_1$. Note that under our assumptions, we have 
$$\max(|w_1 -1|, |w_2 -1|) =\OO\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right),$$
which concludes the proof.
\end{proof}

Combining \eqref{hatw_add1} and \eqref{boundv-w}, we obtain that whp,
\be\label{hatv_add1} 
|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2+\e} 
\ee
Inserting it into \eqref{eq_te_mtl_2task} and using a similar concentration result as in \eqref{boundv-w}, we get whp,
\begin{align}
\te(\hat{\beta}_t^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
{\cor add about the choice of parameters}

### 2020-05-27 writeup/proof_main.tex
lem B.1

Given the optimal ratio $\hat v$, let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix. Denote by ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ the eigenvalues of $\hat{M}^{\top}\hat{M}$. Let $(\hat a_1, \hat a_2)$ be the solutions to the following deterministic equations
	\be
		 \hat a_1 +  \hat a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad  \hat a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac1p\sum_{i=1}^p \frac{ \hat \lambda_i^2 \hat a_1}{ \hat \lambda_i^2\hat a_1 +  \hat a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.\label{eq_a2} \\
		 \ee
		 After obtaining $(\hat a_1,\hat a_2)$, we can solve the following linear equations to get $(\hat a_3,\hat a_4)$:
\begin{gather}
		\left(\rho_2 \hat a_2^{-2}- \hat b_0\right)\cdot \hat  a_3 - \hat b_1 \cdot \hat a_4
		=\hat b_0, \quad \left(\rho_1\hat a_1^{-2} - \hat b_2  \right)\cdot \hat a_4 - \hat b_1 \cdot \hat a_3 =\hat b_1 .\label{eq_a3} 
%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
	\end{gather}
where we denoted
$$\hat b_k:= \frac1{p}\sum_{i=1}^p \frac{\hat \lambda_i^{2k}}{ (\hat a_2 +\hat  \lambda_i^2\hat a_1)^2  },\quad k=0,1,2.$$
Then we introduce the following matrix
$$\Pi = \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot{\hat M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat {M}^{\top}\hat {M}}{(\hat a_2 +\hat  a_1 \hat {M}^{\top}\hat {M})^2} \hat {M}^{\top},$$
which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
We introduce two factors that will appear often in our statements and discussions:
$$\al_-:=(1- \rho_1^{-1/2})^2,\quad \al_+:=(1 + \rho_1^{-1/2})^2.$$ 
In fact, $\al_-^2$ and $\al_+^2$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}. In particular, as $\rho_1$ increases, both $\al_-$ and $\al_+$ will converge to 1 and $Z_1/\sqrt{n_1}$ will be more close to an isometry. Finally, we introduce the error term  
$$\delta:=\frac{\al_+^2 - 1 }{\al_-^{2}} \cdot \kappa^4(\hat M)\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,$$
where we recall that $\kappa(\hat M)$ is the condition number of $\hat M$. Note that this factor converges to 0 as $\rho_1\to \infty$.

@@

Under the simplifying setting in Section \ref{sec_insight}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
\begin{lemma}\label{prop_model_shift_tight}
		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
		$\beta_t$ is a random vector with i.i.d. entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_2$ is a random vector such that $\beta_s - \beta_t$ is a random vector with i.i.d. entries with mean $0$, variance $d^2$ and all moments. Denote
		$\wt \Delta_{\beta} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2)} \bigtr{\Pi}.$
	Then we have
		\begin{align*}
			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2+\oo(1))\cdot \wt \Delta_{\beta}, \\
			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2-\oo(1))\cdot \wt\Delta_{\beta}.
		\end{align*}
\end{lemma}

>>>>

Given the optimal ratio $\hat v$, let $\hat{M} = \hat{v} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix. Denote by ${\hat\lambda}_1\ge {\hat\lambda}_2 \ge \dots \ge {\hat\lambda}_p$ the eigenvalues of $\hat{M}^{\top}\hat{M}$. Let $(\hat a_1, \hat a_2)$ be the solutions to the following deterministic equations
	\be
		 \hat a_1 +  \hat a_2 = 1- \frac{1}{\rho_1 + \rho_2},\quad  \hat a_1 + \frac1{\rho_1 + \rho_2}\cdot \frac1p\sum_{i=1}^p \frac{ \hat \lambda_i^2 \hat a_1}{ \hat \lambda_i^2\hat a_1 +  \hat a_2} = \frac{\rho_1}{\rho_1 + \rho_2}.\label{eq_a2} \\
		 \ee
		 After obtaining $(\hat a_1,\hat a_2)$, we can solve the following linear equations to get $(\hat a_3,\hat a_4)$:
\begin{gather}
		\left(\rho_2 \hat a_2^{-2}- \hat b_0\right)\cdot \hat  a_3 - \hat b_1 \cdot \hat a_4
		=\hat b_0, \quad \left(\rho_1\hat a_1^{-2} - \hat b_2  \right)\cdot \hat a_4 - \hat b_1 \cdot \hat a_3 =\hat b_1 .\label{eq_a3} 
%		\left(\frac{n_1}{\hat a_1^2} -  \sum_{i=1}^p \frac{\hat \lambda_i^4   }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_4 -\left(\sum_{i=1}^p \frac{\hat \lambda_i^2  }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }\right)\hat a_3
%		= \sum_{i=1}^p \frac{\hat \lambda_i^2 }{  (\hat a_2 + \hat \lambda_i^2\hat a_1)^2  }. \label{eq_a4}
	\end{gather}
where we denoted
$$\hat b_k:= \frac1{p}\sum_{i=1}^p \frac{\hat \lambda_i^{2k}}{ (\hat a_2 +\hat  \lambda_i^2\hat a_1)^2  },\quad k=0,1,2.$$
Then we introduce the following matrix
$$\Pi = \frac{\rho_1^2}{(\rho_1 + \rho_2)^2}\cdot{\hat M} \frac{(1 + \hat a_3)\id +\hat  a_4 \hat {M}^{\top}\hat {M}}{(\hat a_2 +\hat  a_1 \hat {M}^{\top}\hat {M})^2} \hat {M}^{\top},$$
which is defined in a way such that {\it in certain sense} it is the asymptotic limit of the random matrix 
$$\hat v\Sigma_1^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2 (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1^{1/2}.$$ 
We introduce two factors that will appear often in our statements and discussions:
$$\al_-(\rho_1):=(1- \rho_1^{-1/2})^2,\quad \al_+(\rho_1):=(1 + \rho_1^{-1/2})^2.$$ 
In fact, $\al_-^2$ and $\al_+^2$ correspond to the largest and smallest singular values of $Z_1/\sqrt{n_1}$, respectively, as given by the famous Mar{\v c}enko-Pastur law \cite{MP}. In particular, as $\rho_1$ increases, both $\al_-$ and $\al_+$ will converge to 1 and $Z_1/\sqrt{n_1}$ will be more close to an isometry. Finally, we introduce the error term  
$$\delta:=\frac{\al_+^2(\rho_1) - 1 }{\al_-^{2}(\rho_1)} \cdot \kappa^4(\hat M)\cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2,$$
where we recall that $\kappa(\hat M)$ is the condition number of $\hat M$. Note that this factor converges to 0 as $\rho_1\to \infty$.

@@

Under the simplifying setting in Section \ref{sec_insight}, we actually have an easier and sharper bound than Theorem \ref{thm_model_shift} as follows. 
\begin{lemma}\label{prop_model_shift_tight}
		In the setting of Theorem \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
		$\beta_t$ is a random vector with i.i.d. entries with mean $0$, variance $\kappa^2$ and all moments, and $\beta_2$ is a random vector such that $\beta_s - \beta_t$ is a random vector with i.i.d. entries with mean $0$, variance $d^2$ and all moments. Denote
		$\wt \Delta_{\beta} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2)} \bigtr{\Pi}.$
	Then we have
		\begin{align*}
			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot \wt \Delta_{\beta}, \\
			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot \wt\Delta_{\beta}.
		\end{align*}
\end{lemma}

### 2020-05-27 writeup/transfer.tex
lem B.1

Theorem \ref{thm_main_informal} shows nearly tight bounds on the trade-off between model-shift bias and variance reduction.
%determined by the covariate shift matrix and the model shift.
The bounds get tighter and tighter as $\rho_1$ increases.
A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{sec_pfmain}.
While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we show that they provide nice interpretation for several simple settings in the rest of the section.

@@

\textit{A simplifying setting.}\label{ex_basic}
	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks. For the noises, we assume that $\e_i$ has i.i.d. entries with mean zero and variances $\sigma_i^2$, $i=1,2$. 
	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
	%The noise level for both tasks is equal to $\sigma > 0$.
	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.
	For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material.

@@

\begin{proposition}\label{prop_dist_transition}
	In the setting of Example \ref{ex_basic} with $\sigma_1 = \sigma_2 = \sigma$, assume that $\rho_1 > 40$ is a fixed constant.
	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${d^2} < \frac {\sigma^2} {2p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${d^2} \ge \frac {2\sigma^2} {p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

>>>>

Theorem \ref{thm_main_informal} shows nearly tight bounds on the trade-off between model-shift bias and variance reduction.
%determined by the covariate shift matrix and the model shift.
The bounds get tighter and tighter as $\rho_1$ increases.
A formal version of Theorem \ref{thm_main_informal} is presented in Theorem \ref{thm_model_shift} and its proof is presented in Appendix \ref{app_proof_main}.
While the general form of $\Delta_{\vari}$ and $\Delta_{\beta}$ can be quite complex, we show that they provide nice interpretation for several simple settings in the rest of the section.

@@

\textit{A simplifying setting.}\label{ex_basic}
	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks. For the noises, we assume that $\e_i$ has i.i.d. entries with mean zero and variances $\sigma_i^2$, $i=1,2$. 
	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
	%The noise level for both tasks is equal to $\sigma > 0$.
	We have $n_i = \rho_i \cdot p$ data points from each task, for $i = 1, 2$.
	For simplicity, we assume that all the random variables have subexponential decay, while keeping in mind that our results can be applied under weaker moments assumptions as shown in the supplementary material.

@@

\begin{proposition}\label{prop_dist_transition}
	In the simplifying setting with $\sigma_1 = \sigma_2 = \sigma$, assume that $\rho_1 > 40$ is a fixed constant.
	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${d^2} < \frac {\sigma^2} {2p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${d^2} \ge \frac {2\sigma^2} {p} \cdot \Phi(\rho_1, \rho_2)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}
